---
title: "Themed dashboard"
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      heading_font:
        google: Sen
      base_font: 
        google: Prompt
    orientation: rows
    self_contained: false
    vertical_layout: scroll
    source_code: embed
    navbar:
      - { title: "Github", href: "https://github.com/shrish-shete20/weblate", align: right, icon: fa-github}
    css: ["fragments/custom.css"]
    skin:
      header_bg: "#ffffff"
      header_fg: "#000000"
      sidebar_bg: "#00438d"
      sidebar_fg: "#ffffff"
      body_bg: "#f8f9fa"
      body_fg: "#000000"
---

```{r setup, include=FALSE}
library(flexdashboard)
# Install thematic and un-comment for themed static plots (i.e., ggplot2)
# thematic::thematic_rmd()
```


Information
=====================================
Row
---------------------------------------------------------------------------------

### R Translation Weblate Status

:::: {.blackbox data-latex=""}
::: {.center data-latex=""}
<strong>Dashboard Developer</strong>
:::
  <p><h3>Shrish Shete</h3>(<em>Contributor at GSOC 2023</em>)</p>
  <i class="fa-solid fa-circle-info"></i> <b>About</b> : Student at <b>IIT Kanpur</b>,India (Statistics and Data Science)<br>
  <i class="fa-regular fa-envelope"></i> <b>Email</b> : sheteshrish1203@gmail.com<br>
  <i class="fa-brands fa-github"></i> <b>Github</b> : https://github.com/shrish-shete20<br>
  <i class="fa-brands fa-linkedin"></i> <b>Linkedin</b> : https://www.linkedin.com/in/shrish-shete-31a34a249/<br>
::::


### R Translation Weblate Status

:::: {.blackbox data-latex=""}
::: {.centers data-latex=""}
<strong>Mentors</strong>
:::
  <h5 class="Mentor1">Ben Ubah</h5>
  <i class="fa-solid fa-circle-info"></i> <b>About</b> : Mentor at GSOC 2023<br>
    <i class="fa-regular fa-envelope"></i> <b>Email</b> : ubah.ben22@gmail.com<br>
  <h5 class="Mentor2">Gabriel Becker</h5>
  <i class="fa-solid fa-circle-info"></i> <b>About</b> : Mentor at GSOC 2023<br>
    <i class="fa-regular fa-envelope"></i> <b>Email</b> : gabembecker@gmail.com<br>
::::

<style>
    .centers {
        text-align: center;
    }
</style>

Row
---------------------------------------------------------------------------------

### <small> <em>About the Dashboard</em></small>

This R project seeks to develop a dashboard that provides a clear overview of the current
status of language translations, enabling the R community to comprehend the progress
made thus far easily.
The development of this tool has the potential to serve as a primary resource for exploring
and comprehending the progress made in translating a specific language. It can benefit a
wide range of stakeholders, including community developers and organizers seeking
information on language translations.
By providing a comprehensive report on the translation status of messages in different
languages, the tool can support the planning of diversity packages and recognize the
contributions of regional volunteers who devote considerable time and effort to translating
messages into their native languages by acknowledging the efforts.

The project aims to establish a robust framework for monitoring the translation status of R.

<i class="fa-solid fa-star"></i> <strong> Features</strong>

- Leaderboard Page : 









<i class="fa-solid fa-toolbox"></i> <strong>TOOLS</strong>

- <i class="fa-solid fa-wrench"></i> Front-End : HTML <i class="fa-brands fa-html5"></i>,CSS <i class="fa-brands fa-css3-alt"></i>,Java Script <i class="fa-brands fa-js"></i>,bslib theme template <i class="fa-solid fa-code"></i>.
- <i class="fa-solid fa-wrench"></i> Back-End : A small ETL infrastructure based on R <i class="fa-brands fa-r-project"></i>,Github actions <i class="fa-brands fa-github"></i>, Github Pages <i class="fa-brands fa-square-github"></i> that daily retrieves data from Weblate API. This infrastructure provides a way to work with Weblate's authentication system automatically. The back-end is completely separated from the front-end.

<i class="fa-solid fa-address-book"></i> <strong>Contact</strong>
If you have any questions, feedback, suggestions, please open an issue on GitHub <i class="fa-brands fa-github"></i> here: https://github.com/shrish-shete20/weblate or email the primary maintainer: sheteshrish1203@gmail.com   

```{r}
htmltools::tags$div(
  htmltools::tags$button(
    id = "view_code",
    class = "btn btn-primary",
    style = "background-color: blue;",
    htmltools::tags$i(class = "fa fa-github"),
    "View Code",
    onclick = "window.open('https://github.com/shrish-shete20/weblate', '_blank')"
  ),
  htmltools::tags$button(
    id = "submit_issue",
    class = "btn btn-danger",
    style = "background-color: red;",
    htmltools::tags$i(class = "fa-solid fa-circle-exclamation"),
    "Submit Issue",
    onclick = "window.open('https://github.com/shrish-shete20/weblate/issues', '_blank')"
  )
)

```